---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
dt <- cs_uncorrelated

dt = dt[1:5000,];
print(dim(dt));


nobs = 5000; 		#	Number of observations in data set
nvar = 5;			  #	Number of variables
nc = 5;			    #	Number of alternatives


# Utility Specification below

atrAlt1 <- cbind(dt$x01,dt$x02,dt$x03,dt$x04,dt$x05);
atrAlt2 <- cbind(dt$x06,dt$x07,dt$x08,dt$x09,dt$x10);
atrAlt3 <- cbind(dt$x11,dt$x12,dt$x13,dt$x14,dt$x15);
atrAlt4 <- cbind(dt$x16,dt$x17,dt$x18,dt$x19,dt$x20);
atrAlt5 <- cbind(dt$x21,dt$x22,dt$x23,dt$x24,dt$x25);


dtaX <- cbind(atrAlt1,atrAlt2,atrAlt3,atrAlt4,atrAlt5);
dtaCh <- cbind(dt$f1,dt$f2,dt$f3,dt$f4,dt$f5);            # The dummy variable indicating twhather the alternative is the chosen
dtaChNum = (apply(dtaCh,1,function(x) which(x==1)));            



appdel = kronecker(matrix(1,1,nc-1),dtaCh);
appdel_tplt =  matrix(nrow=0,ncol=nc*(nc-1));
for(inc in 1:nc)
{
  appdel_tplt_row = matrix(nrow=1,ncol=0);
  for(jnc in 1:nc)
  {
    if(jnc != inc)
    {
      temp = matrix(0,nrow=1,ncol=nc);
      temp[1,jnc] = 1;
      appdel_tplt_row = cbind(appdel_tplt_row,temp);
    }
  }
  appdel_tplt = rbind(appdel_tplt,appdel_tplt_row);
}
appdel1 = appdel_tplt[dtaChNum,];
appdel = t(appdel);
appdel1 = t(appdel1);
appdiff =  appdel -  appdel1;
  
ID = 0.5*diag(nc-1) + 0.5*matrix(1,nrow=nc-1,ncol=nc-1);

outProd = 0;  finalIter <<- 0;

bInit = c(0,0,0,0,0,1,1,1,1,1);

seed10 = 10000;

finalIter <<- 0; tic(); 
res1 <- optim(bInit,lpr,lgd,method="BFGS",control = list(maxit=100, trace=3, fnscale=-1, REPORT=1), hessian = TRUE);
print(res1);  toc();

finalIter = 1;  tic();
res2 <- optim(res1$par,lpr,lgd,method="BFGS",control = list(maxit=1, trace=3, fnscale=-1, REPORT=1));
print(res2);   toc();

cov2 =  solve(res1$hessian) %*% outProd %*% solve(res1$hessian)/nobs/nobs  ;

estimate = res1$par;
stdErr = (sqrt(diag(cov2)));

print(cbind(estimate,stdErr));
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
